VISUALIZATION OF THE RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL

### 2019-10-16 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
improved the fractional part of paper

\section{Examples}
Consider the following fractional integral:
\begin{equation}
\label{eq:ex1_raw}
_0I_t^{\alpha} f(t) = \frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \tau(t-\tau)^{\alpha-1}~d\tau. 
\end{equation}
The function $f(t) = t$ is depicted in Fig.~\ref{fig:geo1}. Let us first convert 
the above integral into a Riemann-Stieltjes integral (see Section~\ref{??}):
\begin{equation}
_0I_t^{\alpha} f(t)=\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \int_0^t f(\tau)~d\,\widetilde{g}_t^{\alpha}(\tau). 
\end{equation}

We can now convert the above Riemann-Stieltjes integral into a Cavalieri integral (see Section~\ref{??}):
\begin{equation}
\label{eq:ex1}
_0I_t^{\alpha} f(t) = \int_0^t f(\tau)~dg_t^{\alpha}(\tau)=\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau,
\end{equation}
with $a_t^{\alpha}(y) = y - \frac{t^{\alpha}-(t-y)^{\alpha}}{\Gamma(\alpha+1)}$ and $b_t^{\alpha}(y) = a_t^{\alpha}(y) + \frac{t^{\alpha}}{\Gamma(\alpha+1)}$. Note, it turns out that for this example $a=a'=C=0$.

@@

\noindent
If we set the value of $\alpha$ to $\sfrac{4}{5}$ and the value of $t$ to 10 in Eq.~\eqref{eq:ex1} we obtain:
\begin{equation}
\label{eq:ex1_specific}
_0I_{10}^{\sfrac{4}{5}} f(t) = \int_{a_{10}^{\sfrac{4}{5}}(y)}^{b_{10}^{\sfrac{4}{5}}(y)} f(\tau)~d\tau = A_{10}^{\sfrac{4}{5}}. 
\end{equation}
Let $R_{10}^{\sfrac{4}{5}}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{10}^{\sfrac{4}{5}}(y)$. The region $R_{10}^{\sfrac{4}{5}}$ is depicted in the right-most panel of Fig.~\ref{fig:geo1}. It is the largest of all the regions depicted in the right-most panel of Fig.~\ref{fig:geo1}. Moreover, let $A_{10}^{\sfrac{4}{5}}$ denote the area of $R_{10}^{\sfrac{4}{5}}$. When we evaluate Equation~\ref{eq:ex1_specific} we obtain $A_{10}^{\sfrac{4}{5}}$ (see Section~\ref{??}). Furthermore, note that dashed grey curves in the right-most panel of Fig.~\ref{fig:geo1} are translations of $b_{10}^{\sfrac{4}{5}}(y)$.\\

@@

\noindent
Let $\mathsf{T}=\{2,4,6,8,10\}$. Varying both $\alpha$ and $t$ results in Eq.~\eqref{eq:ex1}. In contrast with Eq.~\eqref{eq:ex1_specific}, Eq.~\eqref{eq:ex1} can be associated with more than one region. 
Let $R_{t}^{\alpha}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\alpha}(y)$. Note that $b_{t}^{\alpha}(y)$ forms the 
right-most edge of $R_{t}^{\alpha}$. Moreover, let $A_{t}^{\alpha}$ denote the area of $R_{t}^{\alpha}$ and let $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}=\{R_t^{\alpha}|t\in\mathsf{T},~\alpha\in\mathsf{A}\}$. When we evaluate Eq.~\eqref{eq:ex1} we obtain $A_{t}^{\alpha}$ (see Section~\ref{??}). The regions in the set $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}$ are depicted in Fig.~\ref{fig:geo1}. The regions that are depicted in each of the panels of Fig.~\ref{fig:geo1} were generated by varying $t$, whilst keeping the value of $\alpha$ fixed. The title of each panel indicates which $\alpha$-value was used to generate the regions depicted in each panel. The only difference between the regions located in each 
panel is their right edges. The right edges of the regions in each panel are depicted using varying shades of gray. The lighter the shade with which an edge is depicted, 
the larger the $t$-value is that is associated with it.\\

@@

\noindent
Let us now consider a different fractional integral:
\begin{equation}
\label{eq:ex2}
\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \sqrt{\tau}(t-\tau)^{\alpha-1}~d\tau. 
\end{equation}
The non-static non-rectangular infinitesimal-based geometric interpretation associated with Eq.~\eqref{eq:ex1} is depicted in Fig.~\ref{fig:geo2}. 
If we evaluate the integral in Eq.~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ we obtain the curves in the right-most column of Table~\ref{tab:eval}. 
These curves are depicted in Fig~\ref{fig:eval2}.
The validity of the non-static non-rectangular infinitesimal-based geometric interpretation depicted in Fig.~\ref{fig:geo2} is corroborated by Fig.~\ref{fig:eval2}.

>>>>

\section{Examples}
Consider the following fractional integral:
\begin{equation}
\label{eq:ex1_raw}
_0I_t^{\alpha} f(t) = \frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \tau(t-\tau)^{\alpha-1}~d\tau. 
\end{equation}
The function $f(t) = t$ is depicted in Fig.~\ref{fig:geo1}. We can now convert the above fractional integral into a Cavalieri integral (see Section~\ref{??}):
\begin{equation}
\label{eq:ex1}
_0I_t^{\alpha} f(t) = \int_0^t f(\tau)~d\,\widetilde{g}_t^{\alpha}(\tau)=\int_0^t f(\tau)~d\,g_t^{\alpha}(\tau)=\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau,
\end{equation}
with $a_t^{\alpha}(y) = y - \frac{t^{\alpha}-(t-y)^{\alpha}}{\Gamma(\alpha+1)}$, $b_t^{\alpha}(y) = a_t^{\alpha}(y) + \frac{t^{\alpha}}{\Gamma(\alpha+1)}$ and $C=0$.
Note, that for this example $a'=a=0$.\\

@@

\noindent
If we set the value of $\alpha$ to $\sfrac{4}{5}$ and the value of $t$ to 10 in Eq.~\eqref{eq:ex1} we obtain:
\begin{equation}
\label{eq:ex1_specific}
_0I_{10}^{\sfrac{4}{5}} f(t) = \int_{a_{10}^{\sfrac{4}{5}}(y)}^{b_{10}^{\sfrac{4}{5}}(y)} f(\tau)~d\tau = A_{10}^{\sfrac{4}{5}}. 
\end{equation}
Let $R_{10}^{\sfrac{4}{5}}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{10}^{\sfrac{4}{5}}(y)$. The region $R_{10}^{\sfrac{4}{5}}$ is depicted in the right-most panel of Fig.~\ref{fig:geo1}. It is the largest of all the regions depicted in the right-most panel of Fig.~\ref{fig:geo1}. Moreover, let $A_{10}^{\sfrac{4}{5}}$ denote the area of $R_{10}^{\sfrac{4}{5}}$. When we evaluate Equation~\ref{eq:ex1_specific} we obtain $A_{10}^{\sfrac{4}{5}}$ (see Section~\ref{??}). The region $R_{10}^{\sfrac{4}{5}}$ is not bounded by $a_{10}^{\sfrac{4}{5}}(y)$, since $a'=a=0$. Furthermore, note that dashed grey curves in the right-most panel of Fig.~\ref{fig:geo1} are translations of $b_{10}^{\sfrac{4}{5}}(y)$.\\

@@

\noindent
Let $\mathsf{T}=\{2,4,6,8,10\}$. Varying both $\alpha$ and $t$ results in Eq.~\eqref{eq:ex1}. In contrast with Eq.~\eqref{eq:ex1_specific}, Eq.~\eqref{eq:ex1} can be associated with more than one region. 
Let $R_{t}^{\alpha}$ denote the region which is bounded by the $\tau$-axis, the function $f(\tau)$ and the function $b_{t}^{\alpha}(y)$. Note that $b_{t}^{\alpha}(y)$ forms the 
right-most edge of $R_{t}^{\alpha}$. The region $R_{t}^{\alpha}$ is not bounded by $a_{t}^{\alpha}(y)$, since $a'=a=0$. Moreover, let $A_{t}^{\alpha}$ denote the area of $R_{t}^{\alpha}$ and let $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}=\{R_t^{\alpha}|t\in\mathsf{T},~\alpha\in\mathsf{A}\}$. When we evaluate Eq.~\eqref{eq:ex1} we obtain $A_{t}^{\alpha}$ (see Section~\ref{??}). The regions in the set $\mathsf{R}_{\mathsf{T}}^{\mathsf{A}}$ are depicted in Fig.~\ref{fig:geo1}. The regions that are depicted in each of the panels of Fig.~\ref{fig:geo1} were generated by varying $t$, whilst keeping the value of $\alpha$ fixed. The title of each panel indicates which $\alpha$-value was used to generate the regions depicted in each panel. The only difference between the regions located in each 
panel is their right edges. The right edges of the regions in each panel are depicted using varying shades of gray. The lighter the shade with which an edge is depicted, 
the larger the $t$-value is that is associated with it.\\

@@

\noindent
Let us now consider a different fractional integral:
\begin{equation}
\label{eq:ex2}
\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \sqrt{\tau}(t-\tau)^{\alpha-1}~d\tau. 
\end{equation}
We can now convert the above fractional integral into a Cavalieri integral (see Section~\ref{}):
\begin{equation}
\label{eq:ex2_cav}
_0I_t^{\alpha} f(t) = \int_0^t f(\tau)~d\,\widetilde{g}_t^{\alpha}(\tau)=\int_0^t f(\tau)~d\,g_t^{\alpha}(\tau)=\int_{a_t^{\alpha}(y)}^{b_t^{\alpha}(y)} f(\tau)~d\tau,
\end{equation}
with $a_t^{\alpha}(y) = y^2 - \frac{t^{\alpha}-(t-y^2)^{\alpha}}{\Gamma(\alpha+1)}$, $b_t^{\alpha}(y) = a_t^{\alpha}(y) + \frac{t^{\alpha}}{\Gamma(\alpha+1)}$ and $C=0$.
Note, that for this example $a'=a=0$. The non-static non-rectangular infinitesimal-based geometric interpretation associated with Eq.~\eqref{eq:ex1}, which we construct vby employing Eq, is depicted in Fig.~\ref{fig:geo2}. If we evaluate the integral in Eq.~\eqref{eq:ex1} for all $\alpha\in \mathsf{A}$ we obtain the curves in the right-most column of Table~\ref{tab:eval}. These curves are depicted in Fig~\ref{fig:eval2}.
The validity of the non-static non-rectangular infinitesimal-based geometric interpretation depicted in Fig.~\ref{fig:geo2} is corroborated by Fig.~\ref{fig:eval2}.
